---
title: "fNIRS_Analysis"
study: "SJ Training"
author: "AJK"
date: '2024-01-30'
output: html_document
---

### Load data

```{r setup}
library(tidyverse)
library(ggpubr)
library(rstatix)
library(dplyr)
library(lme4)
library(broom)
library(outliers)
```

```{r load data}

#Load the data
setwd("~/PycharmProjects/fnirs-analysis/results")
df_cha <- read.csv("df_cha.csv") 

#Select for HbO and make the predictors categorical
df_cha_hbo <- df_cha %>%
  filter(Chroma %in% "hbo") 
df_cha_hbo$day <- factor(df_cha_hbo$day)
df_cha_hbo$subject <- factor(df_cha_hbo$subject)
df_cha_hbo$Condition <- factor(df_cha_hbo$Condition)
df_cha_hbo$group <- factor(df_cha_hbo$group)
df_cha_hbo$ch_name <- factor(df_cha_hbo$ch_name)

#Look at the data
p <- ggplot(df_cha_hbo, aes(x=ch_name, y=theta)) +
  geom_point(aes(color=ch_name, alpha=0.5)) +
  facet_wrap(~subject) +
  labs(title = "All Data") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
  guides(alpha = "none", color="none")

print(p)
```

The theta weights for participants 202, 204, 206, and 214 look more noisy than the others.

### Outlier Test

```{r}
z_scores_theta <- scale(df_cha_hbo$theta)
outliers <- abs(z_scores_theta) > 3
df_cha_hbo_clean <- subset(df_cha_hbo, !outliers)
nrow(df_cha_hbo) - nrow(df_cha_hbo_clean)
(nrow(df_cha_hbo) - nrow(df_cha_hbo_clean))/nrow(df_cha_hbo)

#Look at the data
p <- ggplot(df_cha_hbo_clean, aes(x=ch_name, y=theta)) +
  geom_point(aes(color=ch_name, alpha=0.5)) +
  facet_wrap(~subject) +
  labs(title = "All Data") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
  guides(alpha = "none", color="none") +
  ylim(-2.5e-06,2.5e-06)

print(p)

```

1.886544% of datapoints (286 out of 15160) had a z-score\>3. The data look more consistent between subjects if we remove outliers.

I'll analyze the data with the outliers first.

### LMM for Channel x Condition

Let's see if we can match the channel x condition interactions in R with the ones from the Python code.

```{r LME1}
# Fixed effects for channel:condition and random effect for subject
library(lme4)
library(dplyr)
model <- lmer(theta ~ -1 + ch_name:Condition + (1|subject), data = df_cha_hbo)
coefficients_summary <- summary(model)$coefficients 
p_values <- coefficients_summary[, "Pr(>|t|)"]
# FDR Correction
adjusted_p_values <- p.adjust(p_values, method = "fdr")
tidy_results <- data.frame(
  variable = rownames(coefficients_summary),
  p_value = p_values,
  fdr_corrected = adjusted_p_values)
sig_ch_cond <- tidy_results %>% filter(fdr_corrected < 0.05)
print(sig_ch_cond)
```

There are 5 significant channels here, but 11 significant channels from the Python output in "ch_model_corrected.csv" :/

### LMM for Group x Day

Now let's assess whether there's a group x day interaction using the same model:

```{r LMER}

# Fixed effects for group:day
model <- lmer(theta ~ -1 + group:day + (1|subject), data = df_cha_hbo)
coefficients_summary <- summary(model)$coefficients 
p_values <- coefficients_summary[, "Pr(>|t|)"]
# FDR Correction
adjusted_p_values <- p.adjust(p_values, method = "fdr")
tidy_results <- data.frame(
  variable = rownames(coefficients_summary),
  p_value = p_values,
  fdr_corrected = adjusted_p_values)
sig_group_day <- tidy_results %>% filter(fdr_corrected < 0.05)
print(sig_group_day)

# Fixed effects for group:day:channel
model <- lmer(theta ~ -1 + group:day:ch_name + (1|subject), data = df_cha_hbo)
coefficients_summary <- summary(model)$coefficients 
p_values <- coefficients_summary[, "Pr(>|t|)"]
# FDR Correction
adjusted_p_values <- p.adjust(p_values, method = "fdr")
tidy_results <- data.frame(
  variable = rownames(coefficients_summary),
  p_value = p_values,
  fdr_corrected = adjusted_p_values)
sig_group_day_ch <- tidy_results %>% filter(fdr_corrected < 0.05)
print(sig_group_day_ch)

# Fixed effects for group:day:channel:condition
#model <- lmer(theta ~ -1 + group:day:ch_name:Condition + (1|subject), data = df_cha_hbo)
#coefficients_summary <- summary(model)$coefficients 
#p_values <- coefficients_summary[, "Pr(>|t|)"]

```

There is no significant interaction between group and day, but there is a significant group x day x channel interaction for: S12_D24, S14_D26, S16_D26, S17_D13, S19_D8, S23_D8, S26_D13, S3_D6

My laptop took too long to evaluate the group x day x channel x condition interaction, so we will skip this for now.

### RM-ANOVA for Significant Channels

Instead of linear mixed models, let's try running a repeated-measures ANOVA on each of the significant channels using the within factors "day" and "condition" & the between factor "group".

**S10_D22:**

```{r ANOVA S10_D22}
# Select channel
ch_S10_D22 <- df_cha_hbo %>%
  filter(ch_name %in% c("S10_D22 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch_S10_D22, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table

```

**S12_D24**

```{r ANOVA S12_D24}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S12_D24 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table

```

**S14_D26**

```{r ANOVA S14_D26}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S14_D26 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table

```

**S16_D26**

```{r ANOVA S16_D26}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S16_D26 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table

```

**S17_D13**

```{r ANOVA S17_D13}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S17_D13 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table

```

**S19_D8**

```{r ANOVA S19_D8}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S19_D8 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table

```

**S20_D7**

```{r ANOVA S20_D7}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S20_D7 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table
```

**S21_D6**

```{r ANOVA S21_D6}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S21_D6 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table
```

**S23_D12**

```{r ANOVA S23_D12}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S23_D12 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table
```

**S23_D8**

```{r ANOVA S23_D8}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S23_D8 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table
```

**S26_D13**

```{r ANOVA S26_D13}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S26_D13 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table
```

**S3_D6**

```{r ANOVA S3_D6}
# Select channel
ch <- df_cha_hbo %>%
  filter(ch_name %in% c("S3_D6 hbo"))
# Run ANOVA
res.aov <- anova_test(
  data = ch, dv = theta, wid = subject,
  within = c(day, Condition), between = c(group))
anova_table <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- anova_table[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
anova_table$adjusted_pval <- adjusted_p_values
anova_table
```

There was a significant effect of [group]{.underline} on S10_D22 (p=0.038) and S14_D26 (p=0.044).

There was a significant effect of [condition]{.underline} on S20_D7 (p=0.021).

There was a significant [group\*condition]{.underline} interaction effect on S10_D22 (p=0.033).

However, none of these survived FDR correction.

### RM-ANOVA for Significant Channels: Auditory

What if we focus on the significant channel/condition combos?

I will use the cleaned dataset with no extreme outliers here.

```{r}
#### Channel 53 - Auditory
ch53_A <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S17_D13 hbo") & Condition %in% c("A"))

# Repeated Measures ANOVA
res.aov <- anova_test(
  data = ch53_A, dv = theta, wid = subject,
  within = c(day), between = c(group))
get_anova_table(res.aov)

# Plot
ggplot(ch53_A, aes(x=day, y=theta)) +
  geom_boxplot() +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1.5) +
  facet_wrap(~group) +
  labs(title = "Ch53 - Auditory") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 


#### Channel 60 - Auditory
ch60_A <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S19_D8 hbo") & Condition %in% c("A"))

# ANOVA
res.aov <- anova_test(
  data = ch60_A, dv = theta, wid = subject,
  within = c(day), between = c(group))
get_anova_table(res.aov)

# Plot
ggplot(ch60_A, aes(x=day, y=theta)) +
  geom_boxplot() +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1.5) +
  facet_wrap(~group) +
  labs(title = "Ch60 - Auditory") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 


```

For Ch53, the **group:day** interaction p=0.050 uncorrected, p=0.078 corrected.

We could also compare across days and within groups using paired t-tests:

```{r}
# Paired T-Test Within Groups
ch53_A_t <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S17_D13 hbo") & Condition %in% c("A") & group %in% c("trained"))
df_wide <- tidyr::pivot_wider(ch53_A_t, names_from = day, values_from = theta)
paired_t_test <- t.test(df_wide$`1`, df_wide$`3`, paired = TRUE)
print(paired_t_test)

ch53_A_c <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S17_D13 hbo") & Condition %in% c("A") & group %in% c("control"))
df_wide <- tidyr::pivot_wider(ch53_A_c, names_from = day, values_from = theta)
paired_t_test <- t.test(df_wide$`1`, df_wide$`3`, paired = TRUE)
print(paired_t_test)

```

p=0.08 for the Ch53-A paired t-test

### RM-ANOVA for Significant Channels: Audiovisual

```{r}
#### Channel 31 - Audiovisual
ch31_AV <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S10_D22 hbo") & Condition %in% c("AV"))

# ANOVA
res.aov <- anova_test(
  data = ch31_AV, dv = theta, wid = subject,
  within = c(day), between = c(group))
model <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- model[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
model$adjusted_pval <- adjusted_p_values
model

# Plot
ggplot(ch31_AV, aes(x=day, y=theta)) +
  geom_boxplot() +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1.5) +
  facet_wrap(~group) +
  labs(title = "Ch31 - Audiovisual") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 


#### Channel 32 - Audiovisual
ch32_AV <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S11_D19 hbo") & Condition %in% c("AV"))

# ANOVA
res.aov <- anova_test(
  data = ch32_AV, dv = theta, wid = subject,
  within = c(day), between = c(group))
get_anova_table(res.aov)

# Plot
ggplot(ch32_AV,  aes(x=day, y=theta)) +
  geom_boxplot() +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1.5) +
  facet_wrap(~group) +
  labs(title = "Ch32 - Audiovisual") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 


#### Channel 41 - Audiovisual
ch41_AV <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S13_D24 hbo") & Condition %in% c("AV"))

# ANOVA
res.aov <- anova_test(
  data = ch41_AV, dv = theta, wid = subject,
  within = c(day), between = c(group))
get_anova_table(res.aov)

# Plot
ggplot(ch41_AV, aes(x=day, y=theta)) +
  geom_boxplot() +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1.5) +
  facet_wrap(~group) +
  labs(title = "Ch41 - Audiovisual") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 

```

For the Ch31-AV **group** effect, p=0.006 uncorrected and p=0.018

```{r}
# Paired T-Test Within Groups
ch31_AV_t <- ch31_AV %>%
  filter(group %in% c("trained"))
df_wide <- tidyr::pivot_wider(ch31_AV_t, names_from = day, values_from = theta)
paired_t_test <- t.test(df_wide$`1`, df_wide$`3`, paired = TRUE)
print(paired_t_test)

ch31_AV_c <- ch31_AV %>%
  filter(group %in% c("control"))
df_wide <- tidyr::pivot_wider(ch31_AV_c, names_from = day, values_from = theta)
paired_t_test <- t.test(df_wide$`1`, df_wide$`3`, paired = TRUE)
print(paired_t_test)

```

No significant changes with paired t-tests.

### RM-ANOVA for Significant Channels: Visual

```{r}
#### Channel 9 - Visual
ch9_V <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S3_D6 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch9_V, dv = theta, wid = subject,
  within = c(day), between = c(group))
get_anova_table(res.aov)

#### S23_D12 
ch74_V <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S23_D12 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch74_V, dv = theta, wid = subject,
  within = c(day), between = c(group))
get_anova_table(res.aov)

#### S18_D27
ch_S18_D27 <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S18_D27 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch_S18_D27, dv = theta, wid = subject,
  within = c(day), between = c(group))
model <- get_anova_table(res.aov)
# Multiple comparisons correction
p_values <- model[["p"]]
adjusted_p_values <- p.adjust(p_values, method = "fdr")
model$adjusted_pval <- adjusted_p_values
model
# Plot
ggplot(ch_S18_D27, aes(x=day, y=theta)) +
  geom_boxplot() +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1.5) +
  facet_wrap(~group) +
  labs(title = "Ch57 - Visual") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 

#### S14_D26
ch_S14_D26 <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S14_D26 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch_S14_D26, dv = theta, wid = subject,
  within = c(day), between = c(group))
model <- get_anova_table(res.aov)
model

#### S15_D14
ch_S15_D14 <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S15_D14 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch_S15_D14, dv = theta, wid = subject,
  within = c(day), between = c(group))
model <- get_anova_table(res.aov)
model

#### S16_D26
ch_S16_D26 <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S16_D26 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch_S16_D26, dv = theta, wid = subject,
  within = c(day), between = c(group))
model <- get_anova_table(res.aov)
model

#### S16_D27
ch_S16_D27 <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S16_D27 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch_S16_D27, dv = theta, wid = subject,
  within = c(day), between = c(group))
model <- get_anova_table(res.aov)
model

#### S3_D6
ch_S3_D6 <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S3_D6 hbo") & Condition %in% c("V"))
# ANOVA
res.aov <- anova_test(
  data = ch_S3_D6, dv = theta, wid = subject,
  within = c(day), between = c(group))
model <- get_anova_table(res.aov)
model

# Plot VO channels
VO_channels1 <- df_cha_hbo_clean %>%
           filter(ch_name %in% c("S3_D6 hbo", 
                        "S23_D12 hbo", 
                        "S14_D26 hbo")  & 
                    Condition %in% c("V"))

VO_channels2 <- df_cha_hbo_clean %>%
           filter(ch_name %in% c(
                        "S16_D26 hbo",
                        "S16_D27 hbo", 
                        "S18_D27 hbo")  & 
                    Condition %in% c("V"))

ggplot(VO_channels1, aes(x=day, y=theta)) +
  geom_boxplot() +
  facet_grid(ch_name ~ group, scales = 'free') +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1) +
  labs(title = "") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 12),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 

ggplot(VO_channels2, aes(x=day, y=theta)) +
  geom_boxplot() +
  facet_grid(ch_name ~ group, scales = 'free') +
  geom_line(aes(group=subject, color=subject, alpha=0.8), 
            linewidth=1) +
  labs(title = "") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 12),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 


```

There was a significant interaction with **day** in S18_D27 (p=0.044) during the visual block but not after FDR correction (p=0.132).

We could also compare across days and within groups using paired t-tests:

```{r}
# Paired T-Test Within Groups
ch57_V_t <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S18_D27 hbo") & Condition %in% c("V") & group %in% c("trained"))
df_wide <- tidyr::pivot_wider(ch57_V_t, names_from = day, values_from = theta)
paired_t_test <- t.test(df_wide$`1`, df_wide$`3`, paired = TRUE)
print(paired_t_test)

ch57_V_c <- df_cha_hbo_clean %>%
  filter(ch_name %in% c("S18_D27 hbo") & Condition %in% c("V") & group %in% c("control"))
df_wide <- tidyr::pivot_wider(ch57_V_c, names_from = day, values_from = theta)
paired_t_test <- t.test(df_wide$`1`, df_wide$`3`, paired = TRUE)
print(paired_t_test)

```

No significant changes within groups.

### Ignore; random stuff

```{r V2_analysis}

V2_AO <- df_cha_hbo %>%
  filter(ch_name %in% c("S13_D25 hbo",
                        "S14_D26 hbo",
                        "S15_D11 hbo",
                        "S15_D14 hbo",
                        "S15_D25 hbo",
                        "S16_D14 hbo",
                        "S16_D25 hbo",
                        "S16_D26 hbo",
                        "S16_D27 hbo",
                        "S17_D13 hbo",   #Ch53
                        "S17_D14 hbo",
                        "S17_D27 hbo",
                        "S18_D26 hbo",
                        "S18_D27 hbo",
                        "S23_D12 hbo",
                        "S24_D11 hbo",
                        "S25_D11 hbo",
                        "S25_D12 hbo",
                        "S25_D13 hbo",
                        "S25_D14 hbo",
                        "S26_D12 hbo",
                        "S26_D13 hbo")  
         & Condition %in% c("A"))

# ANOVA
res.aov <- anova_test(
  data = V2_AO, dv = theta, wid = subject,
  within = c(day), between = c(group))
get_anova_table(res.aov)

# Subgroup Analyses
V2_AO_t <- df_cha_hbo_AVAV %>%
  filter(group %in% c("trained"))
res.aov <- anova_test(
  data = V2_AO_t, dv = theta, wid = subject,
  within = c(ch_name), between = c(day))
get_anova_table(res.aov)

V2_AO_c <- df_cha_hbo_AVAV %>%
  filter(group %in% c("control"))
res.aov <- anova_test(
  data = V2_AO_t, dv = theta, wid = subject,
  within = c(ch_name), between = c(day))
get_anova_table(res.aov)
                                 
# Plot
ggplot(V2_AO, aes(x=day, y=theta)) +
  geom_boxplot() +
  geom_point(aes(color=subject, alpha=0.5), position = "jitter", size=0.8) +
#  geom_line(aes(group=subject, color=ch_name, alpha=0.5), linewidth=1) +
  facet_wrap(~group) +
  labs(title = "Secondary Visual Cortex - Auditory") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 


```

```{r sig_plots, echo=FALSE}

# Day x Group ########
ggplot(df_cha_hbo, aes(x=group, y=theta, color=day)) +
  geom_boxplot() +
#  geom_point(aes(alpha=0.5), position = "jitter", size=0.8) +
#  geom_line(aes(group=subject, color=ch_name, alpha=0.5), linewidth=1) +
  facet_wrap(~Condition) +
  labs(title = "Secondary Visual Cortex - Auditory") +
  geom_hline(yintercept = 0, linetype = 3) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14),
        ) +
   guides(alpha = "none") 

# Day x Condition x Channel ########
bxp <- ggboxplot(df_cha_hbo, x = "day", y = "theta", 
                 color="Condition",
                 add = "jitter", 
                 facet.by = "ch_name",
                 add.params = list(size = 1, alpha = 0.5),  
                 ) +
#  theme(legend.position = "None") +
  ylim(-2e-07,2e-07) +
  geom_hline(yintercept = 0, linetype = 3)
bxp

# Group x Condition x Channel ########
bxp <- ggboxplot(sig_chs, x = "group", y = "theta", 
                 color="Condition",
                 add = "jitter", 
                 facet.by = "ch_name",
                 add.params = list(size = 1, alpha = 0.5),  
                 ) +
#  theme(legend.position = "None") +
  ylim(-2e-07,2e-07) +
  geom_hline(yintercept = 0, linetype = 3)
bxp


# Group x Channel ##########
bxp <- ggboxplot(sig_chs, x = "group", y = "theta", 
                 add = "jitter", 
                 facet.by = "ch_name",
                 add.params = list(size = 1, alpha = 0.5, color="Condition"),  
                 ) +
#  theme(legend.position = "None") +
  ylim(-2e-07,2.5e-07) +
  geom_hline(yintercept = 0, linetype = 3)
bxp

# Condition x Channel ##########
bxp <- ggboxplot(sig_chs, x = "Condition", y = "theta", 
                 color = "Condition",
                 add = "jitter", 
                 facet.by = "ch_name",
                 add.params = list(size = 1, alpha = 0.5),  
                 ) +
#  theme(legend.position = "None") +
  ylim(-2e-07,2e-07) +
  geom_hline(yintercept = 0, linetype = 3)
bxp


# Not Significant:
# Day x Group
bxp <- ggboxplot(sig_chs, x = "day", y = "theta",
  add = "jitter", 
  facet.by = "group") +
  geom_hline(yintercept = 0, linetype = 3) +
  labs(title="Sig Chs") +
  ylim(-4e-07,1e-07)
bxp
# Day x Group x Condition
bxp <- ggboxplot(sig_chs, x = "day", y = "theta", 
                 color="Condition",
                 add = "jitter", 
                 facet.by = "group",
                 add.params = list(size = 1, alpha = 0.5),  
                 ) +
#  theme(legend.position = "None") +
  ylim(-5e-07,5e-07) +
  geom_hline(yintercept = 0, linetype = 3)
bxp
```

## 
